---
title: "Untitled"
output: github_document
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

```{r setup, include=FALSE}
library("worcs")
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
# load_data()
knitr::opts_chunk$set(echo = TRUE)
```

This manuscript uses the Workflow for Open Reproducible Code in Science [@vanlissaWORCSWorkflowOpen2020] to ensure reproducibility and transparency. All code <!--and data--> are available at <git@github.com:noltinho/MyRepository.git>.

This is an example of a non-essential citation [@@vanlissaWORCSWorkflowOpen2020]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

<!--The function below inserts a notification if the manuscript is knit using synthetic data. Make sure to insert it after load_data().-->
`r notify_synthetic()`

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
# inspect dataset before imputation
md.pattern(ca.imputation)
imp <- mice(ca.imputation, maxit=0, print=F)

flux <- flux(ca.imputation)
out.flux <- row.names(flux)[flux$outflux < 0.5] # OpinionPak is excluded

out.log <- imp$loggedEvents # No peculiar variables present
out <- unique(c(out.flux,out.log))

ca.imputation2 <- ca.imputation[, !names(ca.imputation) %in% out]

# remove variable totwt from set of predictors
pred <- make.predictorMatrix(ca.imputation2)
pred
pred[, "totwt"] <- 0
pred

# remove variables OpinionRussia and TrustGov_M
ca.imputation2 <- subset(ca.imputation2, select=-c(OpinionRussia,Region_M))

# change imputation method for ordinal variables
meth <- make.method(ca.imputation2)
meth
meth[c("NetComp","nextyear_M","Statements1","CanBuy_M","TodayEcSit_M")] <- "polr"
meth

# perform multiple imputation
imp <- mice(ca.imputation2, method=meth, predictorMatrix=pred, maxit=5, seed=123)
imp$loggedEvents
imp <- mice.mids(imp, maxit=5)

# inspect convergences
plot(imp)

# specify survey design with imputed data
imp_list <- lapply(1:5 , function(n) complete(imp, action = n))
ca.design.imp <- svydesign(ids=~SamPt, weight=~totwt, data=imputationList(imp_list))

fit <- with(ca.design.imp, svyglm(ThreatHi ~ Gender+AgeGroup2+GeoCode,
                                  family=binomial(link="logit")))

# get response propensities from the imputed data
predm <- with(imp_list, lapply(getfit(fit), predict, type ="response"))

# extract the predicted values and the covariance matrix
pred.values <- MIextract(predm, fun=coef)
cov.matrix <- MIextract(predm, fun=vcov)

# pool the predicted values and add them as variable to the dataframe
pooled.pred <- pool_mi(qhat=pred.values, u=cov.matrix)
ca.imputation2$pooled.est <- summary(pooled.pred)$results

# calculate the averge response propensity
mean(ca.imputation2$pooled.est) # 0.403
hist(ca.imputation2$pooled.est)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
